Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-17 special-issue-ci/Response to reviewers-r2.tex

Previously, we have checked it in grayscale and thought it was OK. We
have done now as instructed.

We would also like to thank this reviewers for his work and helpful
comments.

%-----------------------------------------------------------------------------
\section{Response to Reviewer \#3}

\begin{quote}
\textbf{Please, correct the information about i7-4770
  processor. Additionally, I would recommend to precise the concept of
  safety to ''user's safety'' (or ''voluteer's safety'') in the
  characteristic of the framework (page 5), as you still do not
  address the safety of the system as a whole, at least not at this
  point.}
\begin{quote}

This has been done, as indicated in the response to other reviewers.

\begin{quote}
\textbf{I would also recommend to include at least a short information
  that the system utilizes HTML5 Web Workers, as from my point of view
  it is one of the most important aspects of the framework and to
  reorganize the subsections in section IV and V.}
\end{quote}

Done.

\begin{quote}
\textbf{I would also change the title of the subsection V.A as it begins with ''F15:..'' which is a little bit confusing.}
\end{quote}

Done too. Thanks a lot for your feedback.
